Report on a Safety Checker for Petri nets

### 2014-02-01 paper/workspace/main.tex
bla
Added pseudocode for subprocedure \Delta
Updated paper draft

  # of tokens in place s           >= 0
  # of times transition t is fired >= 0
\end{verbatim}

\begin{verbatim}
* Subprocedure \mathcal{C}:

@@

  # Place equations
  for s in S:
    # initial number of tokens
    print(s + " = " + M0(s))
    for t in T:
      if (t, s) in E and not (s, t) in E:
        # input transition
        print(" + " + t)
      if (s, t) in E and not (t, s) in E:
        # output transition
        print(" - " + t)
    print("\n")

  # Non-negativity conditions
  for s in S:
    print(s + " >= 0\n")
  for t in T:
    print(t + " >= 0\n")
\end{verbatim}

@@

@@

@@

  # Trap implications
  for s in S:
    print(s + " => true")
    for t in s*:
      print(" /\ ( false")
      for p in t*:
        print(" \/ " + p)
     print(")")
    print("\n")

  # Initially marked
  print("false")
  for s in S:
    if M0(s) > 0:
      print(" \/ " + s)
  print("\n")

  # Unmarked in A
  for s in S:
    if A(s) = 0:
      print("~" + p + "\n")
\end{verbatim}

@@

The method Invariant constructs an invariant \verb=I= for given Petri net \verb=N= and \verb=P= when \verb=N= never violates \verb=P=.
We present the method Invariant by example on a simplified mutual exclusion algorithm by Delzanno2001.

@@

\newpage
\begin{verbatim}
* Example:
  - Dual state constraints C':

    - nc - m + cs1 <= 0
    - nc - m + cs2 <= 0
      nc + m - cs1 <= 0
      nc + m - cs2 <= 0

    2 \cdot nc + m < 2 \cdot target1

    Non-negativity conditions:

    target1 >= 0
    nc      >= 0
    m       >= 0
    cs1     >= target1
    cs2     >= target1

@@

    target1 = 1
    nc      = 0
    m       = 1
    cs1     = 1
    cs2     = 1

@@

    cs1 + cs2 + m <= 1

>>>>

  # of tokens in place s           >= 0
  # of times transition t is fired >= 0

* Subprocedure \mathcal{C}:

@@

  \end{verbatim}
\begin{align*}
  C =& \left( \bigwedge_{s \in S}
    s = M_0(s) + \sum_{t \in ^\bullet s} t - \sum_{t \in s^\bullet} t
  \right) \land \\
  & \left( \bigwedge_{s \in S} s \ge 0 \right) \land
    \left( \bigwedge_{t \in T} t \ge 0 \right)
\end{align*}

@@

\begin{verbatim}

@@

\end{verbatim}
\begin{align*}
  C_\theta =& \left( \bigwedge_{s \in S} \left( s \Rightarrow
        \bigwedge_{t \in s^\bullet} \bigvee_{p \in t^\bullet} p
    \right) \right) \land \\
  & \left( \bigvee_{s \in S: M_0(s) > 0} s \right) \land \\
  & \left( \bigwedge_{s \in S: A(s) > 0} \neg s \right) \\
\end{align*}
\begin{verbatim}

@@

\end{verbatim}
\begin{align*}
  & \delta = \left( \sum_{A_\theta(s)} s \ge 0 \right)\\
\end{align*}

@@

The method Invariant constructs an invariant \verb=I= for given Petri net \verb=N= and \verb=P= when \verb=N= never violates \verb=P=.

@@

\newpage
\begin{verbatim}
* Example:

  - With weakened property P \/ (\neg \delta)

  - Negated property is \neg P /\ \delta

  - Dual state constraints C':
    0 >= (- cs1) + id1 + idle1 + (- nid1)
    0 >= (- id1) + (- idle1) + nid1 + req1
    0 >= cs1 + (- req1)
    0 >= after_you2 + (- req2)
    0 >= (- after_you2) + await2 + id2
    0 >= (- await2) + idle2
    0 >= cs2 + (- req2)
    0 >= (- cs2) + id2 + idle2
    0 >= (- id2) + (- idle2) + req2

    id1 + id2 + idle1 + idle2 < 2 * target_1 + trap_1

    id1        >= trap_1
    cs1        >= target_1
    idle1      >= 0
    req1       >= trap_1
    nid1       >= 0
    id2        >= trap_1
    cs2        >= target_1
    idle2      >= 0
    req2       >= trap_1
    after_you2 >= trap_1
    await2     >= 0
    target_1   >= 0
    trap_1     >= 0

@@

    id1        = 1
    cs1        = 1
    idle1      = 0
    req1       = 1
    nid1       = 0
    id2        = 1
    cs2        = 1
    idle2      = 0
    req2       = 1
    await2     = 0
    after_you2 = 1
    target_1   = 1
    trap_1     = 1

@@

    id1 + id2 + req1 + req2 + after_you2 + cs1 + cs2 <= 2

  - Invariant with trap constraint \delta added:

    id1 + id2 + req1 + req2 + after_you2             >= 1
    id1 + id2 + req1 + req2 + after_you2 + cs1 + cs2 <= 2
